Reproducible Summary Tables with gtsummary

### 2020-12-09 RJtemplate_gtsummary_submission.tex
Updates from Overleaf

\section{Section title in sentence case}

Introductory section which may include references in parentheses
\citep{R}, or cite a reference such as \citet{R} in the text.

\section{Another section}

This section may contain a figure such as Figure~\ref{figure:rlogo}.

\begin{figure}[htbp]
  \centering
  \includegraphics{Rlogo-5}
  \caption{The logo of R.}
  \label{figure:rlogo}
\end{figure}

\section{Another section}

There will likely be several sections, perhaps including code snippets, such as:

\begin{example}
  x <- 1:10
  result <- myFunction(x)
\end{example}

\section{Summary}

This file is only a basic article template. For full details of \emph{The R Journal} style and information on how to prepare your article for submission, see the \href{https://journal.r-project.org/share/author-guide.pdf}{Instructions for Authors}.

>>>>

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{data-summaries}{%
\section{Data Summaries}\label{data-summaries}}

\include{tbl_trial_desc}

\section{test}

\begin{longtable}[]{@{}llll@{}}
\caption{Example data frame, \texttt{trial}}\tabularnewline
\toprule
colname & label & class & values\tabularnewline
\midrule
\endfirsthead
\toprule
colname & label & class & values\tabularnewline
\midrule
\endhead
trt & Chemotherapy Treatment & character & \texttt{Drug\ A},
\texttt{Drug\ B}\tabularnewline
age & Age & numeric & \texttt{6}, \texttt{9}, \texttt{10}, \texttt{17} ,
\ldots{}\tabularnewline
marker & Marker Level (ng/mL) & numeric & \texttt{0.003},
\texttt{0.005}, \texttt{0.013}, \texttt{0.015} , \ldots{}\tabularnewline
stage & T Stage & factor & \texttt{T1}, \texttt{T2}, \texttt{T3},
\texttt{T4}\tabularnewline
grade & Grade & factor & \texttt{I}, \texttt{II},
\texttt{III}\tabularnewline
response & Tumor Response & integer & \texttt{0},
\texttt{1}\tabularnewline
death & Patient Died & integer & \texttt{0}, \texttt{1}\tabularnewline
ttdeath & Months to Death/Censor & numeric & \texttt{3.53},
\texttt{5.33}, \texttt{6.32}, \texttt{7.27} , \ldots{}\tabularnewline
\bottomrule
\end{longtable}
